---
title: "CSE3020 Lab7"
author: "Faraz Suhail"
date: "15/03/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Name: "Faraz Suhail"
## Reg. No.: "19BCE1525"


### 1. Choose number of the cluster centre and no. of clusters

```{r}
library(cluster)
library(ClusterR)
library(ggplot2)
library(factoextra)
library(shipunov)
library(ggfortify)
library(factoextra)
```

```{r}
data = read.csv("protein.csv")
head(data)
```

```{r}
data1 = data[2:10]
set.seed(240)
k = kmeans(data1,centers = 3)
k
```

### 2. Choose the plotting methods for visualizing results

### a.To display Cluster : use plot( )

```{r}
plot(data$RedMeat,data$WhiteMeat,col = k$cluster,xlab="Red Meat",ylab = "White Meat")
text(x=data$RedMeat,y=data$WhiteMeat,data$Country)

plot(data$Eggs,data$Milk,col = k$cluster,xlab="Eggs",ylab = "Milk")
text(x=data$Eggs,y=data$Milk,data$Country)

plot(data$Fish,data$Cereals,col = k$cluster,xlab="Fish",ylab = "Cereals")
text(x=data$Fish,y=data$Cereals,data$Country)

plot(data$Starch,data$Nuts,col = k$cluster,xlab="Starch",ylab = "Nuts")
text(x=data$Starch,y=data$Nuts,data$Country)

plot(data$Nuts,data$Fr.Veg,col = k$cluster,xlab="Nuts",ylab = "Veg")
text(x=data$Nuts,y=data$Fr.Veg,data$Country)


ggplot(data,aes(x=RedMeat,y=WhiteMeat)) + geom_point(aes(color=k$cluster)) + labs(color = "Cluster") + geom_text(aes(label = Country))

ggplot(data,aes(x=Eggs,y=Milk)) + geom_point(aes(color=k$cluster)) + labs(color = "Cluster") +  geom_text(aes(label = Country))

ggplot(data,aes(x=Fish,y=Cereals)) + geom_point(aes(color=k$cluster)) + labs(color = "Cluster") + geom_text(aes(label = Country))

ggplot(data,aes(x=Starch,y=Nuts)) + geom_point(aes(color=k$cluster)) + labs(color = "Cluster") + geom_text(aes(label = Country))

ggplot(data,aes(x=Nuts,y=Fr.Veg)) + geom_point(aes(color=k$cluster)) + labs(color = "Cluster") + geom_text(aes(label = Country))
```


### b. To display cluster centre : library(factoextra) , function : fviz_cluster()

```{r}
fviz_cluster(k,data = data[2:10])
```

### c. Display cluster : use Clustergram(),autoplot()

```{r}
Clustergram(data1,maxcl = 3,nboot = FALSE,method = "kmeans",col = "#deeb34")
autoplot(kmeans(data1,3),data=data1)
```

### d. Analyze all the resulting parameters of Kmeans clustering

```{r}
k$cluster
k$centers
k$totss
k$withinss
k$tot.withinss
k$betweenss
k$size
k$iter
k$ifault
ggplot(k,aes(k$cluster,fill = cluster)) + geom_histogram(stat = "count")  + xlab("Cluster") + ylab("Size")
```

### e. Determining Optimal Clusters

1.Elbow method

2.Silhouette method

3.Gap statistic

```{r}
fviz_nbclust(data1, kmeans, method = "wss") +   geom_vline(xintercept = 4, linetype = 2) + labs(subtitle = "Elbow method")
fviz_nbclust(data1, kmeans, method = "silhouette")+ labs(subtitle = "Silhouette method")
fviz_nbclust(data1, kmeans, nstart = 25,  method = "gap_stat", nboot = 50)+ labs(subtitle = "Gap statistic method")
```
