---
title: "CSE3020 Lab6"
author: "Faraz Suhail"
date: "11/03/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Name: "Faraz Suhail"
## Reg. No.: "19BCE1525"


```{r}
library(igraph)
```

1. Read the given adjacency matrix into R (Adjacency.csv)

2. Read the given edge matrix into R(Edges.csv)

```{r}
matrix = read.csv("Lab6-DataSet_Adjacency.csv")
edge = read.csv("Lab6-DataSet_Edges.csv")
head(matrix)
head(edge)
rownames(matrix) = seq(2000, 2010, length.output = 11)
```

3. Create and plot the graph from the adjacency matrix and edge matrix (customize the vertex color edge size, vertex frame and label)

```{r}
matrix1 = matrix[2:12]
colnames(matrix1) = seq(2000, 2010, length.output = 11) 
head(matrix1)
```

```{r}
matrix1 = data.matrix(matrix1)
head(matrix1)
g = graph_from_adjacency_matrix(matrix1,diag = FALSE) 
plot(g,vertex.color = "#eaff00",vertex.size=30) 
```

```{r}
g2 = graph.empty(n=11)
g2 = add.edges(g2,c(1,2, 2,3, 3,5, 4,5, 5,4, 5,3, 7,9, 7,8, 9,11, 9,1, 11,1)) 
plot(g2,vertex.label=c(2000,2001,2002,2003,2004,2005,2006, 2008,2010),vertex.color = "#eaff00",vertex.size=25)
```

4. Display the edges & vertices, the network as matrix and the names of vertices

```{r}
print(E(g))
print(V(g))
```

5. Find the count of vertices and edges of the created graph

```{r}
print(E(g2))
print(V(g2))
```

6. Display the adjacency vertices of each vertex(individual) in the created graph

7. Find the min and max degree of the created graph

```{r}
print(get.adjacency(g))
print(get.adjacency(g2))
V(g)$names = seq(2000,2010) 
V(g2)$names = c(2000,2001,2002,2003,2004,2005,2006,2008,2010) 
print(V(g)$names)
print(V(g2)$names)
print(vcount(g))
print(ecount(g))
print(vcount(g2))
print(ecount(g2))
print(get.adjedgelist(g))
print(get.adjedgelist(g2))
```


8. Create & set vertex attribute property named profit and values(“+”, “-”, “+”, “-”, “+”, “-”,“+”, “-”, “+”)

```{r}
V(g)$profit =c("+", "-", "+", "-", "+", "-","+","-","+") 
print(V(g)$profit)
V(g2)$profit =c("+", "-", "+", "-", "+", "-","+","-","+") 
print(V(g2)$profit)
```

9. Create & set vertex attribute property named type and values(either leap or non-leap year)

```{r}
V(g)[(names %% 4)==0]$type = "leap" 
V(g)[(names %% 4)!=0]$type = "non-leap" 
V(g2)[(names %% 4)==0]$type = "leap"
V(g2)[(names %% 4)!=0]$type = "non-leap" 
print(V(g)$type)
print(V(g2)$type)
```

10. Create & set edge attribute named weight and values (if edge exits in between leap year vertices then 5 else 1 )

```{r}
g = delete_vertex_attr(g,"names") 
E(g)$weight = 1
E(g2)$weight= 1
E(g)[21]$weight=5 
E(g)[41]$weight=5 
E(g)[42]$weight=5
E(g2)[9]$weight = 5
```

11. Convert the created un-directed graph into directed graph based on the following rule:

a. edge directed towards high value vertex

b. if any one of the vertex is leap year then put the reverse edge with same weight

12. Display the adjacency matrix of the resultant directed graph.

```{r}
plot(g,edge.color = E(g)$weight,vertex.size=20,edge.width=E(g)$weight,vertex.color="#c8ff00")

plot(g2,edge.color = E(g2)$weight,vertex.size=20,edge.width=E(g2)$weight,vertex.color="#c8ff00")
```


13. Display the in-degree and out-degree of each vertex of resultant directed graph

```{r}
print(get.adjacency(g))
print(get.adjacency(g2))
print(degree(g,mode="in")) 
print(degree(g,mode="out")) 
print(degree(g2,mode="in")) 
print(degree(g2,mode="out"))
```