---
title: "CSE3020 Lab3"
author: "Faraz Suhail"
date: "08/02/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Name: "Faraz Suhail"
## Reg. No.: "19BCE1525"

```{r}
#Import libraries
library(ggplot2)
library(ggExtra)
library("tidyverse")
```
### Ques i. Construct of Scatterplot, Scatterplot With Encircling, Jitter Plot, Counts Chart, Bubble plot using R

```{r}
#ScatterPlot 
orange <- data("Orange")
gg<-ggplot(Orange,aes(x=age,y=circumference))+ geom_point()+ geom_smooth(method="loess",se=F)+ 
    labs(subtitle="Age Vs Circumference",y="Circumference", x="Age", title="Scatterplot") 
plot(gg)
```


```{r}
#Jitter Plot
plotj <- ggplot(Orange, aes(age, circumference)) + geom_point() + geom_smooth(method="lm", se=F) + 
     labs(subtitle="Orange: age vs circumference", y="hwy", x="cty", title="Jitterplot", caption="Source: Orange")
plot(plotj)
```

```{r}
# Counts Plot 
gc <- ggplot(Orange, aes(age, circumference)) + geom_count(col="tomato3", show.legend=F) + 
  labs(subtitle="Orange: age vs circumference", y="Circumference", x="Age", title="Counts Plot")
plot(gc)
```

```{r}
#Histogram 
o<-Orange
theme_set(theme_bw()) 
o_select<-o[o$age>=400 & o$age<1500, ]
g<- ggplot(o,aes(age,circumference))+geom_count()+geom_smooth(method="lm",se=F) 
ggMarginal(g, type = "histogram", fill="red")
ggMarginal(g, type = "boxplot", fill="orange")
```

### Ques ii. Statistical Model using R with Orange dataset:

### 1. Look at Orange using head. What type of data are each of the columns?

```{r}
head(Orange)
str(orange)
sapply(Orange,class)
```
### 2. Find the mean, standard deviation, and standard error of tree circumference.
```{r}
#mean
mean(Orange$circumference)
#standard deviation
sd(Orange$circumference)
#standard error
sqrt(length(Orange$circumference))
```
### 3. Make a linear model which describes circumference (the response) as a function of age (the predictor). Save it as an object with <-, then print the object out by typing its name. What do those coefficients mean?

```{r}
#linear model describing the circumference as a function of age.
model<-lm(circumference~age, data=Orange) 
model
```
Coefficients are estimates of the unknown population parameters and describe the relationship between a predictor variable and the response. 

### 4. Make another linear model describing age as a function of circumference. Save this as a different object.
```{r}
#linear model describing age as a function of circumference
model2<-lm(age~circumference,data=Orange) 
model2
```

### 5. Call summary() on both of your model objects. What do you notice?
```{r}
summary(model)
summary(model2)
```


### Ques 6. Does this mean that trees growing makes them get older? Does a tree getting older make it grow larger? Or are these just correlations?

### Ans: Yes, the trees are growing larger as they get older as evident by the coeffient being positive which means that the age is directly propotion to circumference.


### Ques 7. Does the significant p value prove that trees growing makes them get older? Why not?

### Ans: The p value is very small which means that there is no correlation and the hypothesis can be rejected.