---
title: "CSE3020 Lab5"
author: "Faraz Suhail"
date: "02/03/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Name: "Faraz Suhail"
## Reg. No.: "19BCE1525"

```{r}
library("TTR")
library(forecast)
library(magick)
library(ggplot2)
library(dplyr)
```

```{r}
india <- read.csv("covid_india.csv")
india$Date <- as.Date(india$Date,"%d-%b-%y")
head(india)
```

### 1). You want to predict the last year monthly, weekly trend based on the RTPCR response, (i.e.) No. of +Ve cases and No. –Ve cases along with admitted and discharged trend.

```{r}
ggplot(india, aes(x=Date, y=Daily.Confirmed)) +
  geom_line() + xlab("") + ylim(0, 500000)

ggplot(india, aes(x=Date, y=Daily.Deceased)) +
  geom_line() + xlab("") + ylim(0, 5000)

ggplot(india, aes(x=Date, y=Daily.Recovered)) +
  geom_line() + xlab("") + ylim(0, 500000)
```

### 2). Identify the death rate due to Covid-19

```{r}
india$death.rate<- india$Daily.Deceased / india$Daily.Confirmed
deathRatetotal = max(india$Total.Deceased, na.rm = TRUE) / max(india$Total.Confirmed, na.rm = TRUE)
print("Total death rate: ")
print(deathRatetotal)
```

### 3). Compare the last year and this year trends with respect to 1st , 2nd and 3rd wave also forecast the 4th Wave impact in India

```{r}
ggplot(india, aes(x=Date, y=Daily.Confirmed)) +
  geom_line() + ylab("2020 Daily Confirmed") + scale_x_date(limits = as.Date(c("2020-01-30", "2020-12-31")))
ggplot(india, aes(x=Date, y=Daily.Confirmed)) +
  geom_line() + ylab("2021 Daily Confirmed") + scale_x_date(limits = as.Date(c("2021-01-01", "2021-10-31")))
```
```{r}
ggplot(india, aes(x=Date, y=Daily.Deceased)) +
  geom_line() + ylab("2020 daily Confirmed") + scale_x_date(limits = as.Date(c("2020-01-30", "2020-12-31")))

ggplot(india, aes(x=Date, y=Daily.Deceased)) +
  geom_line() + ylab("2021 daily Confirmed") + scale_x_date(limits = as.Date(c("2021-01-01", "2021-10-31")))

```
```{r}
ggplot(india, aes(x=Date, y=Daily.Recovered)) +
  geom_line() + ylab("2020 daily Recovered") + scale_x_date(limits = as.Date(c("2020-01-30", "2020-12-31")))

ggplot(india, aes(x=Date, y=Daily.Recovered)) +
  geom_line() + ylab("2021 daily Recovered") + scale_x_date(limits = as.Date(c("2021-01-01", "2021-10-31")))
```

##### Inference: Wave 2 in 2021 is intensive i.e., sharp rise in confirmed cases, recovered cases and deceased cases is seen in all aspects, making these 2 waves alot similiar to each other except their intensity of affect


```{r}
fit <- auto.arima(india$Daily.Confirmed)
forecastedValues <- forecast(fit, 31)

plot(forecastedValues, main = "Graph with forecasting of upcoming Wave Daily cases Confirmed",
col.main = "blue") 

fit <- auto.arima(india$Daily.Deceased)
forecastedValues <- forecast(fit, 31)

plot(forecastedValues, main = "Graph with forecasting of upcoming Wave Daily Deceased",
col.main = "blue") 
 

fit <- auto.arima(india$Daily.Recovered)
forecastedValues <- forecast(fit, 31)
  
plot(forecastedValues, main = "Graph with forecasting of upcoming Wave Daily Recovered",
col.main = "blue") 
 
```

### 4). Construct the model using the Simple moving average, Exponential Moving Average and ARIMA to forecast the Covid19 Dataset.

```{r}
#Simple moving average
SMA1 <- SMA(india$Daily.Confirmed,n=31)
plot.ts(SMA1,ylab="SMA Daily Confirmed prediction",
col.main = "blue")

#Exponential Moving Average
ema <-EMA(india$Daily.Confirmed,n=31)
plot.ts(ema,ylab="EMA Daily Confirmed prediction",
col.main = "blue") 

# ARIMA
fit <- auto.arima(india$Daily.Confirmed)
forecastedValues <- forecast(fit, 31)
  
plot(forecastedValues, ylab = "ARIMA Daily Confirmed prediction",
col.main = "blue") 
```

### 5). Show the all above implementation with the visual impact 

```{r}
fit <- auto.arima(india$Total.Confirmed)
forecastedValues <- forecast(fit, 31)
  
  
plot(forecastedValues, main = "Forecasting of upcoming Wave Total cases Confirmed",
col.main = "blue") 
 
fit <- auto.arima(india$Total.Deceased)
forecastedValues <- forecast(fit, 31)
  
  
plot(forecastedValues, main = "Forecasting of upcoming Wave Total Deceased",
col.main = "blue") 

fit <- auto.arima(india$Total.Recovered)
forecastedValues <- forecast(fit, 31)
  
  
plot(forecastedValues, main = "Forecasting of upcoming Wave Total Recovered",
col.main = "blue") 
```