---
title: "CSE3020 Lab4"
author: "Faraz Suhail"
date: "22/02/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Name: "Faraz Suhail"
## Reg. No.: "19BCE1525"


### 1. Use Breast Cancer Wisconsin data set from the UCI Machine learning repo to plot the PCA analysis. Use the ‘prcomp’ function runs PCA on the data.

```{r}
library(devtools)
library(MASS)
library(ggbiplot)
```

```{r}
data1 <- read.csv("data.csv")
data1<-data1[1:32]
data<-na.omit(data1)
head(data)
```


```{r}
cancer.pca <- prcomp(data[3:32], scale. = TRUE)
print(ggbiplot(cancer.pca, obs.scale = 1, var.scale = 1,
  groups = data$diagnosis, ellipse = TRUE, circle = TRUE) +scale_color_discrete(name = '')
  +theme(legend.direction = 'horizontal', legend.position = 'top'))
```

```{r}
model1 <- lda(diagnosis~., data = data[2:8])
model1
```

```{r}
model2 <- lda(diagnosis~., data = data[2:32])
model2
```

## table of model 1
```{r}
predictions <- predict(model1, data = data[3:8])$class
# summarize accuracy
table(predictions, data$diagnosis)
```

## table of model 2
```{r}
predictions <- predict(model2, data = data[3:32])$class
# summarize accuracy
table(predictions, data$diagnosis)
```

#### Both the models have some difference in their error measurement. The model 2 trained with more variables have more accuracy.


# 2. Use the built-in iris dataset in R to plot the LDA analysis. Use the lda function of the MASS package in R Project the LDA visual output and Compare the LDA and PCA 2D Projection of Iris dataset

```{r}
data(iris)
head(iris)
```

```{r}
r <- lda(formula = Species ~ ., 
         data = iris, 
         prior = c(1,1,1)/3)
```


```{r}
r$prior
r$counts
r$means
r$scaling
r$svd
```

```{r}
prop = r$svd^2/sum(r$svd^2)
prop
```

```{r}
r2 <- lda(formula = Species ~ ., 
          data = iris, 
          prior = c(1,1,1)/3,
          CV = TRUE)
head(r2$class)
head(r2$posterior)
```

```{r}
train <- sample(1:150, 75)
r3 <- lda(Species ~ ., # training model
          iris, 
          prior = c(1,1,1)/3, 
          subset = train)
plda = predict(object = r, # predictions
               newdata = iris[-train, ])
head(plda$class) # classification result
head(plda$posterior)
head(plda$x) # LD projections
```

```{r}
plda_plot <- cbind(train, data.frame(predict(r3)$x))
spc2=iris[train,]$Species
plda_plot <- cbind(plda_plot,spc2)
ggplot(plda_plot,aes(LD1,LD2)) + geom_point(aes(color=spc2))
```

```{r}
cancer.pca <- prcomp(iris[1:4], scale. = TRUE)
print(ggbiplot(cancer.pca, obs.scale = 1, var.scale = 1,
               groups = iris$Species) + scale_color_discrete(name = '') + theme(legend.direction = 'horizontal', legend.position = 'top'))
```
